# Protocols {#sec-protocols-docs}


```{r setup, include=FALSE}
here::i_am("docs/protocols-docs.qmd")
library(here)
library(tidyverse)
library(gt)
library(reticulate)

source_python(here("designcter/proto.py"))
```


```{r protocols_df_raw, include=FALSE}
protocols_df_raw <- read_csv(here("docs/data/protocols.csv"))
```

```{r protocols_df, include=FALSE}
protocols_df <- protocols_df_raw |> 
  select(exam_name, protocol_name, phase_design_text, contrast_text)
```

```{r filter, include=FALSE}
protocols_df_body <- protocols_df |> filter(exam_name %in% flatten_chr(exam_id_name$Body))

protocols_df_neuro <- protocols_df |> filter(exam_name %in% c(flatten_chr(exam_id_name$Neuro), "CTA Brain", "CTV Brain"))

protocols_df_trauma <- protocols_df |> filter(
  protocol_name %in% c(protocols_id_name$cta_neck_trauma, 
                   protocols_id_name$ct_facial_trauma,
                   protocols_id_name$ct_orbit_trauma,
                   protocols_id_name$pan_scan,
                   protocols_id_name$cta_blunt_abd,
                   protocols_id_name$cta_penetrate_abd,
                   protocols_id_name$cta_chest_trauma,
                   protocols_id_name$ct_second_look_abd)
  )
```

```{r include=FALSE}
exam_id_protocol_id$ct_body_trauma
```


```{r gt_custom, include=FALSE}
# Custom display table
gt_custom <- function(df) {
  df |>
    gt() |>
    sub_missing(missing_text = "---") |> 
    cols_label(
      protocol_name = "Protocol", phase_design_text = "Phase Design",
      contrast_text = "Contrast"
    ) |>
    fmt_markdown(columns = everything()) |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_row_groups()
    ) |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels()
    ) 
    
}
```

```{r gt_custom_body, include=FALSE}
# gt_custom_body <- function(df){
#   gt_custom(df) |> 
#     opt_stylize(style = 6, color = "cyan")
# }
```

The protocols used in this application were adapted from Ramathibodi emergency radiology handbook @erad_book.


## Body CT

### CTWA

```{r protocols_df_body_ctwa_tbl, echo=FALSE}
protocols_df_body_ctwa_tbl <- protocols_df_body |> 
  filter(exam_name == "CTWA") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "cyan")
  

protocols_df_body_ctwa_tbl
```

### CTA Whole Abdomen

```{r protocols_df_body_cta_wa_tbl, echo=FALSE}
protocols_df_body_cta_wa_tbl <- protocols_df_body |> 
  filter(exam_name == "CTA Whole Abd") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "red")

protocols_df_body_cta_wa_tbl
```

### CT Upper Abdomen

```{r protocols_df_body_ctupperabd_tbl, echo=FALSE}
protocols_df_body_ctupperabd_tbl <- protocols_df_body |> 
  filter(exam_name == "CT Upper Abd") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "cyan")

protocols_df_body_ctupperabd_tbl
```

### CT Lower Abdomen

```{r protocols_df_body_ctlowerabd_tbl, echo=FALSE}
protocols_df_body_ctlowerabd_tbl <- protocols_df_body |> 
  filter(exam_name == "CT Lower Abd") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "green")

protocols_df_body_ctlowerabd_tbl
```

### CT KUB


```{r protocols_df_body_ctkub_tbl, echo=FALSE}
protocols_df_body_ctkub_tbl <- protocols_df_body |> 
  filter(exam_name == "CT KUB") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "blue")

protocols_df_body_ctkub_tbl
```

In cases of suspected urothelial or renal tumor:

- The patient should have a full bladder before undergoing a CT scan. 
- Consider clamping the Foley catheter or instilling NSS into the bladder for patients on continuous bladder irrigation (CBI).

### CTA for PE

```{r protocols_df_body_ctape_tbl, echo=FALSE}
protocols_df_body_ctape_tbl <- protocols_df_body |> 
  filter(exam_name == "CTA for PE") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "red")

protocols_df_body_ctape_tbl
```


### CT Chest

```{r protocols_df_body_ctchest_tbl, echo=FALSE}
protocols_df_body_ctchest_tbl <- protocols_df_body |> 
  filter(exam_name == "CT Chest") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "gray")

protocols_df_body_ctchest_tbl
```


### CT Chest + WA

```{r protocols_df_body_ctchestwa_tbl, echo=FALSE}
protocols_df_body_ctchestwa_tbl <- protocols_df_body |> 
  filter(exam_name == "CT Chest + Whole Abd") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "gray")

protocols_df_body_ctchestwa_tbl
```


### CTA Chest 

```{r protocols_df_body_ctachest_tbl, echo=FALSE}
protocols_df_body_ctachest_tbl <- protocols_df_body |> 
  filter(exam_name == "CTA Chest") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "red")

protocols_df_body_ctachest_tbl
```

### CTA Whole Aorta

```{r protocols_df_body_ctawholeaorta_tbl, echo=FALSE}
protocols_df_body_ctawholeaorta_tbl <- protocols_df_body |> 
  filter(exam_name == "CTA Whole Aorta") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "red")

protocols_df_body_ctawholeaorta_tbl
```

### CTA Runoff

```{r protocols_df_body_ctarunoff_tbl, echo=FALSE}
protocols_df_body_ctarunoff_tbl <- protocols_df_body |> 
  filter(exam_name == "CTA runoff") |> select(!exam_name) |> 
  gt_custom() |> 
  opt_stylize(style = 3, color = "red")

protocols_df_body_ctarunoff_tbl
```


## Neuro CT

```{r protocols_df_neuro_tbl, echo=FALSE}
protocols_df_neuro_tbl <- protocols_df_neuro |> 
  gt_custom() |> 
  cols_label(exam_name = "Exam") |> 
  opt_stylize(style = 3, color = "cyan")

protocols_df_neuro_tbl
```

## Trauma CT

```{r protocols_df_trauma_tbl, echo=FALSE}
protocols_df_trauma_tbl <- protocols_df_trauma |> 
  gt_custom() |> 
  cols_label(exam_name = "Exam") |> 
  opt_stylize(style = 3, color = "red")

protocols_df_trauma_tbl
```






